Preliminary Results

### 2019-06-25 documents/preliminary_results.tex
results added plus stats about dataset without outliers

\begin{table*}[h]\centering
    \caption{Statistics about dataset with different sampling techniques}
    %\scriptsize
    \begin{tabular}{l r r r r}%
        \toprule
      &    \textbf{w/o sampling} & \textbf{Online Sampling} & \textbf{Mikolov} & \textbf{w/o outliers}  \\%
        \midrule%
        Min     &   34 & 34 & 34 & \\%
       Max    & 9Mio & 0.36 Mio. & 0.36 Mio & \\%
      	QTR1      & 79 & 79 & 79\\%
         Median &166 & 166 & 166 & \\%
         Mean & 2227 & 1125 & 1125 & \\%
       QTR3     & 533 & 533 & 534 & \\%
       QTR3 + 1.5IQR   & 1214 & 1214 & 1217  \\%
        \bottomrule%
   \end{tabular}%
   \label{tab:stats_pairs}%
\end{table*}
\begin{table*}[h]\centering
    \caption{Statistics about dataset with different sampling techniques}
    %\scriptsize
    \begin{tabular}{l r r r r}%
        \toprule
      &    \textbf{w/o sampling} & \textbf{Online Sampling} & \textbf{Mikolov} & \textbf{w/o outliers}  \\%
        \midrule%
        Size of Ds   (in words)     &  17 Mio.& 17 Mio. & 8 Mio.& \\%
        Number of Pairs       & 141 Mio. & 71 Mio. & 71. Mio & \\%
        Number of Sentences         & 0.8 Mio & 0.8 Mio & 0.4 Mio  \\%
        \bottomrule%
   \end{tabular}%
   \label{tab:sampling_stats}%
\end{table*}
\newpage

@@

\newpage
\section{Batch\_size}
This section shows a plot of the batch size per batch.
\begin{figure}[h!]
\caption{Batch size per batch}
\includegraphics[scale=0.65]{batch_sizes}
\centering
\end{figure}
\section{Results}
Figure shows the results of the training of the text8 dataset without outliers. 
\begin{figure}[h!]
\caption{Results text8 without outliers}
\includegraphics[scale=0.65]{text8_without_outliers}
\centering
\end{figure}

>>>>

\begin{table*}[h]\centering
    \caption{Statistics about dataset with different sampling techniques}
    %\scriptsize
    \begin{tabular}{l r r r r}%
        \toprule
      &    \textbf{w/o sampling} & \textbf{Online Sampling} & \textbf{Mikolov} & \textbf{w/o outliers}  \\%
        \midrule%
        Min     &   34 & 34 & 34 & 7 \\%
       Max    & 9 Mio. & 0.36 Mio. & 0.36 Mio & 590 \\%
      	QTR1      & 79 & 79 & 79&30\\%
         Median &166 & 166 & 166 & 54 \\%
       QTR3     & 533 & 533 & 534 & 123\\%
       QTR3 + 1.5IQR   & 1214 & 1214 & 1217 &227  \\%
               \bottomrule%
       Mean & 2227 & 1125 & 1125 & 100\\%
   \end{tabular}%
   \label{tab:stats_pairs}%
\end{table*}
\begin{table*}[h]\centering
    \caption{Statistics about dataset with different sampling techniques}
    %\scriptsize
    \begin{tabular}{l r r r r}%
        \toprule
      &    \textbf{w/o sampling} & \textbf{Online Sampling} & \textbf{Mikolov} & \textbf{w/o outliers}  \\%
        \midrule%
        Size of Ds   (in words)     &  17 Mio.& 17 Mio. & 8 Mio.& 2.8 Mio.\\%
        Number of Pairs       & 141 Mio. & 71 Mio. & 71. Mio & 6 Mio. \\%
        Number of Sentences         & 0.8 Mio & 0.8 Mio & 0.4 Mio  & 0.1 Mio.\\%
        Vocabulary Size & 0.25 Mio & 0.25 Mio & 0.25 Mio & 0.06 Mio. \\%
        \bottomrule%
   \end{tabular}%
   \label{tab:sampling_stats}%
\end{table*}
\newpage

\begin{figure}
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[scale=0.69]{online_sampling_example}
  \captionof{figure}{Online Sampling}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[scale=0.69]{preprocessing_sampling_example}
  \captionof{figure}{Preprocessing S.}
  \label{fig:test2}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[scale=0.69]{online_sampling_example}
  \captionof{figure}{No Sampling}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

\newpage
\section{Batch\_size}
This section shows a plot of the batch size per batch.
\begin{figure}[h!]
\caption{Batch size per batch}
\includegraphics[scale=0.65]{batch_sizes}
\centering
\end{figure}
\section{Results}
Figure \ref{fig:results_w/o_outliers} shows the results of the training of the text8 dataset without outliers. Those results are to be taken very lightly for two reasons: 
\begin{enumerate}
\item The data set is very small, i.e 60k vocabulary
\item To assess word similarity only 12 words from the data set were taken. As those were the only one that are in the data set without outliers and in the wordsim dataset. 
\end{enumerate}

Figure shows that the deletion of the specific word ``the`` does not hinder performance.

\begin{figure}[h!]
\caption{Results text8 without the word ``the``}
\includegraphics[scale=0.65]{results_without_the}
   \label{fig:results_w/o_outliers}%

\centering
\end{figure}

\begin{figure}[h!]
\caption{Results text8 without outliers}
\includegraphics[scale=0.65]{text8_without_outliers}
   \label{fig:results_w/o_outliers}%

\centering
\end{figure}
